On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-11-28 paper.tex
update 11/28 in Tokyo

%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%
%Kohei
%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%l.168 - 1326

@@

Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2. Assume its seed $\sigma$ consists of $n$ beads.
%Let us denote its transcript by $w = w_1 w_2 w_3 \cdots$ for some $w_1,w_2,w_3 \in \Sigma = \{e\}$.
For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$ that is foldable by $\Xi$. Hence $C_0 = \sigma$.

@@

\begin{theorem}[Tunnel Troll Theorem]
Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$. If there are indices $i$ and $j$ such that $S[i..j+1] = bt^{j-i}b$, then $\#bc(C_i)$ > $\#bc(C_j)$.
\end{theorem}

@@

\proof%{Proof of Tunnel Troll Theorem}
Assume $\Xi$ is deterministic. %How they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section. 
Each of beads in transcript are bound either inside of tunnel or outside (Fig. \ref{TTT_position}). If a bead is stabilized at inside of tunnel, then its successor is already decided the position either inside of a tunnel or outside. Moreover, If a bead is stabilized at outside of a tunnel, then its position is an entrance of a tunnel or otherwise.

Tunnel sections have three possible shape with considering symmetry such as straight, acute turn and obtuse turn (Fig. \ref{TTT_tunnel}). %Let us focus entrances of a tunnel such as $p^\prime$, then Entrances have two possible shape (Fig. \ref{TTT_enterpoint}).

Let us consider each of cases of tunnel A, B, and C. Accordingly, We use lemma \ref{TTT_neighbor_lemma}

\begin{lemma}
\label{TTT_neighbor_lemma}
If a bead does not have any bond, then neighbors of it must be occupied by $\alpha + 2$ beads at $\delta = 1$ and unary except first and last beads.
\end{lemma}

\begin{proof}[lemma \ref{TTT_neighbor_lemma}]
A bead in transcript needs predecessor and successor except first and last beads. If the bead does not have ant bond, then it use hand with $\alpha$ neighbors. Thus, lemma \ref{TTT_neighbor_lemma} is clearly true.
\end{proof}

Let us consider tunnel sections only tunnel A and B. See Fig. \ref{TTT_position}. From appendix (Entrance of Tunnel A, B and Exit of Tunnel), we add maximum number which each transitions provide binding capabilities for each edge where $a$ is number of consuming binding capabilities when the bead is stabilized at position of $successor\ in\ outside$.

%The sequence $S$ can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+ \cup bt^+bt^+$.

Next, we consider on tunnel C section. If $w[i]$ is stabilized by tunnel C and $S[i+1]$ is $t$, then $w[i+1]$ is stabilized by tunnel A or B because if $w[i+1]$ is stabilized by tunnel C, then $C_{i+1}$ is a terminal. Hence, tunnel C section is divided cases such as Figure \ref{TTT_tunnelC_graph}. Cases of $S[i...] = bt^l (l \geq 2)$ are already considered (Upper). According to appendix (Tunnel C), cases of $S[i..i+2] = btb$ also consume some binding capabilities (Lower).

Thus, if a bead is stabilized through a tunnel section, then it consume some binging capabilities.

@@

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (180:1) {$p^\prime$};
            \node[above] at (-1200:1) {$p^\prime$};

@@

    \end{tabular}
    \caption{All possible tunnel sections: straight, acute turn, and obtuse turn}
    \label{TTT_tunnel}
  \end{center}
\end{figure}

%\begin{figure}
%  \begin{center}
%    \begin{tabular}{cc}
%      
%      \begin{minipage}{0.2\hsize}
%      \centering
%        \begin{tikzpicture}
%
%          \begin{scope}[xshift=1cm, yshift=2cm]
%            \fill(0,0) circle [radius=0.1];
%            \node[above] at (180:1.2) {$p^\prime$};
%            
%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
%            
%            
%            \foreach \theta in {120,-120}{
%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
%            }
%
%            \draw[->] (-1.1,0) -- (-0.1,0);
%          \end{scope}
%
%          \node at (0.25,0) {Tunnel A,B};
%        \end{tikzpicture}
%      \end{minipage}
%
%      \begin{minipage}{0.2\hsize}
%      \centering
%        \begin{tikzpicture}
%
%          \begin{scope}[xshift=1cm, yshift=2cm]
%            \fill(0,0) circle [radius=0.1];
%            \node[above] at (180:1.2) {$p^\prime$};
%
%            \draw[transform canvas={shift=(-120:1.2)}](0,0) circle [radius=0.1];
%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
%            
%            
%            \foreach \theta in {120}{
%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
%            }
%
%            \draw[->] (-1.1,0) -- (-0.1,0);
%          \end{scope}
%
%          \node at (0.25,0) {Tunnel C};
%        \end{tikzpicture}
%      \end{minipage}
%
%    \end{tabular}
%    \caption{Entrance of a tunnel}
%    \label{TTT_enterpoint}
%  \end{center}
%\end{figure}

%\begin{figure}
%  \begin{center}
%    \begin{tikzpicture}
%      \draw[thick]
%      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
%      \node at(2.5,1) {Outside};
%      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
%      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};
%
%      
%      
%      \draw[thick]
%      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
%      \node at(10.5,1) {Inside of a tunnel};
%      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
%      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
%
%      \draw[->]
%      (outside) edge [bend left] node[left] {$b$} (enter)
%                edge [loop left] node[left] {$b$} (outside)
%      (enter)   edge [bend left] node[above] {$b$} (next-tunnel)
%                edge [bend left] node[above] {$b$} (next-outside)
%                edge [bend left] node[right] {$b$}  (outside)
%      (next-tunnel) edge         node[right] {$t$} (next-outside)
%                edge [loop right]node[below] {$t$}    (next-tunnel)
%      (next-outside) edge[bend left] node[above] {$t$}  (outside)
%                edge [bend left]     node[above] {$t$}(enter)
%      ;
%      
%    \end{tikzpicture}
%    \caption{Cases on position of a bead}
%    \label{TTT_position1}
%  \end{center}
%\end{figure}

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \draw[thick, gray]
      (0.5,1)--(0,1)--(0,4)--(4,4)--(4,1)--(3.5,1);
      \node at(2,1) {Outside};
      \node at (2,3.2) [rectangle, draw, rounded corners] (enter) {Entrance of a tunnel};
      \node at(2,1.8) [rectangle, draw, rounded corners] (outside) {Otherwise};

      \draw[thick, gray]
      (7.5,1)--(7,1)--(7,4)--(11,4)--(11,1)--(10.5,1);
      \node at(9,1) {Inside of a tunnel};
      \node at(9,3.2) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
      \node at(9,1.8) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};

      \draw[->]
      (outside) edge [bend left, blue] node[left] {$s=b,\Delta=-1$} (enter)
                   edge [loop left, blue] node[below left] {$s=b,\Delta=\pm 0$} (outside)
      (enter)   edge [bend left, blue] node[above] {$s=b,\Delta=-1$} (next-tunnel)
                edge [bend left, blue] node[above] {$s=b,\Delta=-a$} (next-outside)
                edge [bend left, blue] node[right] {$s=b,\Delta=\pm 0$}  (outside)
      (next-tunnel) edge[teal]         node[right] {$s=t,\Delta=-a$} (next-outside)
                edge [loop right, teal]node[right] {$s=t,\Delta=\pm 0$}    (next-tunnel)
      (next-outside) edge[bend left, teal] node[above] {$s=t,\Delta=+a$}  (outside)
                edge [bend left, teal]     node[above] {$s=t,\Delta=+(a-1)$}(enter)
      ;

    \end{tikzpicture}
    \caption{Increment on Tunnel A,B}
    \label{TTT_position}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Outside of tunnels};
      \node at (3.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
      \node at (7,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
      \draw[->] (outside1)--(enter1);
      \draw[->] (enter1)  --(inside1);
      \draw[->] (inside1) --(exit1);

      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
      \node at (3.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
      \node at (7,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
      \draw[->] (outside2)--(enter2);
      \draw[->] (enter2)  --(inside2);
      \draw[->] (inside2) --(exit2);

      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {Outside of tunnels};
      \node at (3.5,1) [rectangle, draw,rounded corners] (enter3)   {Entrance of a tunnel};
      \node at (7,1)   [rectangle, draw, rounded corners] (inside3) {Inside of a tunnel C};
      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {Outside of tunnels};     
      \draw[->] (outside3)--(enter3);
      \draw[->] (enter3)  --(inside3);
      \draw[->] (inside3) --(exit3);

      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {Inside of atunnel};
      \node at (3.5,0) [rectangle, draw,rounded corners] (enter4)   {Entrance of a tunnel};
      \node at (7,0)   [rectangle, draw, rounded corners] (inside4) {Inside of a tunnel C};
      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {Outside of tunnels};     
      \draw[->] (outside4)--(enter4);
      \draw[->] (enter4)  --(inside4);
      \draw[->] (inside4) --(exit4);
    \end{tikzpicture}
    \caption{Case of Tunnel C}
    \label{TTT_tunnelC_graph}
  \end{center}
\end{figure}

\subsection{Appendix of Tunnel Troll Theorem}
\subsubsection{Entrance of TunnelA,B}

Fig.\ref{TTT_tunnel_direction} exhibits all the three kinds of entrance of tunnel A, B.
Any cases in $\delta = 1, \alpha = 2$ consume some binding capabilities into the follows.

\begin{itemize}
\item{Case of $t_0$}\\
  Let us consider points of $n_3,n_4$ either occupied or not. A point $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel. If $n_3$ is free, then $p^\prime$ has to be bound to a bead except $n_1$ due to deterministically stabilize. In this situation, at least three neighbors of $n_1$ are free that is $n_1$ leave at least one bond from lemma \ref{TTT_neighbor_lemma}. Hence, $p^\prime$ must be bound to $n_1$. Thus, a case of $t_0$ consumes two binding capabilities and it does not supply any binding capabilities.

\item{Case of $t_{\pm 60}$}\\
  In this case, a point $n_4$ or $n_5$ is free, too. If $n_5$ is free, $p^\prime$ has to be bound to $n_1$ or $n_2$. If $n_5$ is occupied, then $n_4$ is free. This time, $n_2$ has some binding capabilities so $p^\prime$ has to be bound to $n_2$.

  In this situation, $p^\prime$ is able to supply a binding capability. if this capability is active, $p^\prime$ bind a bead into $n_4$ or $n_5$. However, $n_2$ and $n_3$ are exist in back bone. According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $n_4$ or $n_5$ so this capability is inactive. Thus, a case of $t_{\pm 60}$ consumes some binding capabilities.

\item{Case of $t_{\pm 120}$}\\
  Binding capabilities that $p^\prime$ supply are inactive according to Jordan curve theorem on $n_1$ and $n_2$. Moreover, $p^\prime$ has to be bound to one of $n_3, n_4, n_5$ in order to deterministically stabilize.
Thus, a case of $t_{\pm 120}$ consumes some binging capabilities.

@@

\subsubsection{Exit of Tunnel}

Fig.\ref{TTT_tunnel_exit} exhibits all the two kinds of exit of tunnel. 
At least one of point $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.

\paragraph{$\delta = 1, \alpha = 2$}
 Any cases of $\delta = 1, \alpha = 2$ supply at most $a$ binding capabilities into follows where $a$ is number of predecessor of $p^\prime$ consumes binging capabilities.

\begin{itemize}
\item{Case of $n_1$ and $n_2$ are free}\\
  This case can be regarded same situation as entrance. See Fig.\ref{TTT_tunnel_exit} (Left). Predecessor $n_5$ has to be bound $n_4$ and $n_5$ because each of $n_3$ and $n_4$ leave binding capabilities. Hence, at least $a=2$. This time, $\alpha = 2$ that is this case supply at most only $a$ binding capabilities.

\item{Case of $c$ is occupied}\\
  See Fig.\ref{TTT_tunnel_exit} (Right). If $n_1$ is occupied, then $n_2$ is free so that $n_5$ has to be bound $n_4$. Hence, at least $a=1$. This case can supply two binding capabilities but $p^\prime$ can bind to only one of $n_0$ or $n_2$ because $n_0$ or $n_2$ will be occupied a successor of $p^\prime$. Therefore, this case supply at most only $a=1$ active binding capability.

@@

\paragraph{$\delta = 1, \alpha \geq 3$}
Any cases of $\delta = 1, \alpha \geq 3$ consume some binding capabilities into follows.

@@

\begin{figure}
  \centering
    \begin{tabular}{cc}

      \begin{minipage}{0.48\linewidth}
      \centering
        \begin{tikzpicture}

@@

      \begin{minipage}{0.48\linewidth}
      \centering
        \begin{tikzpicture}

@@

          \node at (0,-2) {Point $n_1$ is occupied};
        \end{tikzpicture}
      \end{minipage}

    \end{tabular}
    \caption{Exit of Tunnel}
    \label{TTT_tunnel_exit}
\end{figure}

\subsubsection{Tunnel C}

Assume $w[i]$ is a bead which stabilized by tunnel C. Let us consider kinds of stabilization $S[i-2..i] = tbt$ or $S[i-2..i] = bbt$ except cases of $w[i]$ is inside of tunnel A, B.

\subsubsection{Case of $S[i-2..i] = tbt$}
Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.

\begin{itemize}
\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
  In this figure, Bead $n_4$ has at least one binding so that $w[i-2]$ has to bound $n_4$. Moreover, $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically. On the other hand, $w[i]$ can supply two bindings but free neighbors of $w[i]$ are two points. One of them is occupied by a successor. Therefore $w[i]$ can only bind one of $n_5, n_6$ that is $w[i]$ supplies at most one binding. Thus, this case consumes some binding capabilities.

\item{Right of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
  This cases are divided on number of capabilities that $w[i-2]$ consumes.
  \begin{itemize}
  \item[-]{$w[i]$ does not consume any bindings}\\
    $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically. $w[i]$ has to be bound to $w[i-2]$ because $w[i-2]$ has bindings. This time, let us consider either $n_4$ is occupied or not. If $n_4$ is occupied, then $w[i-2]$ has no active bindings that is this situation consumes some binding capabilities. If $n_4$ is free and $w[i+1]$ is stabilized in $n_4$, then $w[i-2]$ has to bind $w[i+1]$. Therefore, In this case, stabilization of $w[i-2..i+1]$ consumes some bindings. If $n_4$ is free and $w[i+1]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[i+1]$. Therefore, in this case consumes some bindings. Thus in this cases consume some binding capabilities.

>>>>

%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%
%Kohei
%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%l.177 - 1312

@@

Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2. Assume its seed $\sigma$ consists of $n$ beads.
%Let us denote its transcript by $w = w_1 w_2 w_3 \cdots$ for some $w_1,w_2,w_3 \in \Sigma = \{e\}$.
For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$, that is, foldable by $\Xi$. Hence $C_0 = \sigma$.

@@

\begin{theorem}[Tunnel Troll Theorem]
Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. If there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$, then $\#bc(C_{i-1}) > \#bc(C_j)$ and if $S[i..j+1] = bt^lbt^mb \quad (l + m = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_j)$. On the other hand, at $\delta = 1$ and $\alpha \geq 3$, if S$[k] = t$, then $\#bc(C_{k-1}) > \#bc(C_k)$.
\end{theorem}

@@

\proof%{Proof of Tunnel Troll Theorem}
Assume $\Xi$ is deterministic.
Each bead in the transcript is bound either inside a tunnel or outside. If a bead is stabilized inside a tunnel, then its successor is already decided the position either inside of a tunnel or outside. Moreover, If a bead is stabilized outside a tunnel, then its position is an entrance of a tunnel or otherwise.

Tunnel sections have three possible shapes up to symmetry : straight($A$), obtuse($B$) and acute($C$) turn (Fig. \ref{TTT_tunnel}), and we will consider each of those.

\begin{lemma}
\label{TTT_neighbor_lemma}
For unary transcripts at $\delta = 1$, If a bead has no free hand, then at least $\alpha + 2$ of its neighbors have to be occpied.
\end{lemma}

\begin{lemma}
\label{TTT_entrance_Tab}
Let $\Xi$ be an oritatami system at $\delta = 1, \alpha =2$ 
Assume $\Xi$ stabilizes transcript until $w[i-1]$. If $w[i]$ is stabilized at an entrance point of tunnel $A$ or $B$, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
\end{lemma}

\begin{lemma}
\label{TTT_exit}
Let $w[i]$ be a bead which is stabilized in exit of a tunnel.
At $\delta = 1, \alpha =2$, If we assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$, then $\#bc(C_{h-1}) \geq \#bc(C_i)$ and $\#bc(C_{i-2}) \geq \#bc(C_i)$.
%if we assume $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
On the other hand, if we assume $S[k] = t (k \leq i)$ at $\delta =1, \alpha \geq 3$, then $\#bc(C_{k-1}) > \#bc(C_{k})$.
\end{lemma}

\begin{lemma}
\label{TTT_tunnelC_lemma}
Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. We assume $S[h..i+1] = bt^{(i-h)}b \quad (1<h<i)$. If at least one of $w[h+1..i]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_i)$.
\end{lemma}

Let us first consider cases of $\delta \geq 3, \alpha = 1$. These cases are clearly true because we use lemma\ref{TTT_exit}.

Next, we consider the case of $\delta = 2, \alpha = 1$. We assume there is index $h$ such that $S[h-1..h+1] = bbt$ or $S[h-1..h+1] = tbt$. According to lemma\ref{TTT_entrance_Tab}, if $w[h+1]$ is stabilized by tunnel $A$ or $B$, then $\#bc(C_{h-1}) > \#bc(C_{h})$. Also,  According to lemma\ref{TTT_exit}, if $w[h+1]$ is stabilized by tunnel $C$, then $\#bc(C_{h-1}) > \#bc(C_{h})$, too.
On the other hand, if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$. Therefore, if there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$ or $S[i..j+1] = bt^mbt^nb \quad (m + n = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_{j})$.

\qed

@@

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (180:1) {$p^\prime$};
            \node[above] at (-120:1) {$p^\prime$};

@@

    \end{tabular}
    \caption{All possible tunnel sections: straight, obtuse turn, and acute turn}
    \label{TTT_tunnel}
  \end{center}
\end{figure}

%\begin{figure}
%  \begin{center}
%    \begin{tikzpicture}
%      \draw[thick, gray]
%      (0.5,1)--(0,1)--(0,4)--(4,4)--(4,1)--(3.5,1);
%      \node at(2,1) {Outside};
%      \node at (2,3.2) [rectangle, draw, rounded corners] (enter) {Entrance of a tunnel};
%      \node at(2,1.8) [rectangle, draw, rounded corners] (outside) {Otherwise};
%
%      
%      
%      \draw[thick, gray]
%      (7.5,1)--(7,1)--(7,4)--(11,4)--(11,1)--(10.5,1);
%      \node at(9,1) {Inside of a tunnel};
%      \node at(9,3.2) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
%      \node at(9,1.8) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
%
%      \draw[->]
%      (outside) edge [bend left, blue] node[left] {$s=b,\Delta=-1$} (enter)
%                   edge [loop left, blue] node[below left] {$s=b,\Delta=\pm 0$} (outside)
%      (enter)   edge [bend left, blue] node[above] {$s=b,\Delta=-1$} (next-tunnel)
%                edge [bend left, blue] node[above] {$s=b,\Delta=-a$} (next-outside)
%                edge [bend left, blue] node[right] {$s=b,\Delta=\pm 0$}  (outside)
%      (next-tunnel) edge[teal]         node[right] {$s=t,\Delta=-a$} (next-outside)
%                edge [loop right, teal]node[right] {$s=t,\Delta=\pm 0$}    (next-tunnel)
%      (next-outside) edge[bend left, teal] node[above] {$s=t,\Delta=+a$}  (outside)
%                edge [bend left, teal]     node[above] {$s=t,\Delta=+(a-1)$}(enter)
%      ;
%      
%    \end{tikzpicture}
%    \caption{Increment on Tunnel A,B}
%    \label{TTT_position}
%  \end{center}
%\end{figure}

%\begin{figure}
%  \begin{center}
%    \begin{tikzpicture}
%      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Outside of tunnels};
%      \node at (3.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
%      \node at (7,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
%      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
%      \draw[->] (outside1)--(enter1);
%      \draw[->] (enter1)  --(inside1);
%      \draw[->] (inside1) --(exit1);
%      
%      
%      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
%      \node at (3.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
%      \node at (7,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
%      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
%      \draw[->] (outside2)--(enter2);
%      \draw[->] (enter2)  --(inside2);
%      \draw[->] (inside2) --(exit2);
%
%      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {Outside of tunnels};
%      \node at (3.5,1) [rectangle, draw,rounded corners] (enter3)   {Entrance of a tunnel};
%      \node at (7,1)   [rectangle, draw, rounded corners] (inside3) {Inside of a tunnel C};
%      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {Outside of tunnels};     
%      \draw[->] (outside3)--(enter3);
%      \draw[->] (enter3)  --(inside3);
%      \draw[->] (inside3) --(exit3);
%
%      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {Inside of atunnel};
%      \node at (3.5,0) [rectangle, draw,rounded corners] (enter4)   {Entrance of a tunnel};
%      \node at (7,0)   [rectangle, draw, rounded corners] (inside4) {Inside of a tunnel C};
%      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {Outside of tunnels};     
%      \draw[->] (outside4)--(enter4);
%      \draw[->] (enter4)  --(inside4);
%      \draw[->] (inside4) --(exit4);
%    \end{tikzpicture}
%    \caption{Case of Tunnel C}
%    \label{TTT_tunnelC_graph}
%  \end{center}
%\end{figure}

\begin{proof}[lemma \ref{TTT_neighbor_lemma}]
A transcript bead in has predecessor and successor except the first and last beads. If the bead does not have any free hand, then it uses hands with $\alpha$ neighbors. Thus, lemma \ref{TTT_neighbor_lemma} is clearly true.
\end{proof}

\begin{proof}[lemma \ref{TTT_entrance_Tab}]
Fig.\ref{TTT_tunnel_direction} exhibits all the three kinds of entrance of tunnel A, B.
Let $w[i]$ be stabilized at an entrance point of Tunnel $A$ or $B$.
All cases are $\#bc(C_{i-1}) > \#bc(C_{i})$ as follows.

\begin{itemize}
\item{Case of $t_0$}\\
  Let us consider points $n_3,n_4$. At least one of the points $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel. If $n_3$ is free, then $p^\prime$ has to be bound to a bead other than $n_1$ due to deterministically stabilize. In this situation, at least three neighbors of $n_1$ are free, that is, $n_1$ has at least one free hand from lemma \ref{TTT_neighbor_lemma}. Hence, $p^\prime$ must be bound to $n_1$. Thus, a case of $t_0$ consumes two hands and it does not supply any binding capabilities.

\item{Case of $t_{\pm 60}$}\\
  In this case, a point $n_4$ or $n_5$ is free, too. If $n_5$ is free, $p^\prime$ has to be bound to $n_1$ or $n_2$. If $n_5$ is occupied, then $n_4$ is free. This time, $n_2$ has some free hands so $p^\prime$ has to be bound to $n_2$.

  In this situation, $p^\prime$ is able to supply a binding capabilities which could $p^\prime$ bind a bead into $n_4$ or $n_5$. However, $n_2$ and $n_3$ are part of a contiguous conformation. According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $n_4$ or $n_5$ so this capability is inactive. Thus, a case of $t_{\pm 60}$ is$\#bc(C_{i-1}) > \#bc(C_{i})$.

\item{Case of $t_{\pm 120}$}\\
  Binding capabilities that $p^\prime$ supplies are inactive according to Jordan curve theorem on $n_1$ and $n_2$. Moreover, $p^\prime$ has to be bound to one of $n_3, n_4, n_5$ in order to deterministically stabilize.
Thus, a case of $t_{\pm 120}$ is $\#bc(C_{i-1}) > \#bc(C_{i})$.

@@

\end{proof}

\begin{proof}[lemma \ref{TTT_exit}]
Fig.\ref{TTT_tunnel_exit} exhibits all the two kinds of exit of tunnel. 
At least one of points $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.

\begin{paragraph}{}
$\delta = 1, \alpha = 2$\\
Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$. We assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$.
If let $a$ be $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$ as follows. Also, if $h - i > 1$ and let $j$ be $h<j<i$, then $\#bc(C_{j-1}) \geq \#bc(C_{j})$ because any neighbors of $w[j]$ are occupied by beads of tunnel so that any $w[i+1..]$ cannot reach neighbors of $w[j]$. Thus, $\#bc(C_{h-1}) \geq \#bc(C_i)$ and $\#bc(C_{i-2}) \geq \#bc(C_i)$.
\end{paragraph}

\begin{itemize}
\item{Case of $n_1$ and $n_2$ being free}\\
  This case can be regarded the same as entrance. See Fig.\ref{TTT_tunnel_exit} (Left). Predecessor $n_5$ has to be bound to $n_4$ and $n_5$ because both of $n_3$ and $n_4$ have binding capabilities. Hence, $a \geq 2$. This time, $\alpha = 2$, that is, this case $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.

\item{Case of $n_1$ is occupied}\\
  See Fig.\ref{TTT_tunnel_exit} (Right). If $n_1$ is occupied, then $n_2$ is free so that $n_5$ has to be bound $n_4$. Hence,  $a \geq 1$. This case can supply two binding capabilities but $p^\prime$ can bind to only one of $n_0$ or $n_2$ because $n_0$ or $n_2$ will be occupied by the successor of $p^\prime$. Therefore, this case $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.

@@

\begin{paragraph}{}
$\delta = 1, \alpha \geq 3$\\
Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha \geq 3$. We assume $w[i]$ is stabilized at exit of tunnel.
Any cases $\#bc(C_{i-1}) > \#bc(C_{i})$. Moreover, if $S[k] = t (k \leq i)$, then $\#bc(C_{k-1}) > \#bc(C_{k})$ because both of sides of the path $p$ in Fig.\ref{TTT_inside_tunnel} ($n_1, n_2$) have two free points and one of $n_1, n_2$ is not the predecessor so that it has hand and moreover that $w[k]$ supplies any binding capabilities because its neighbors are occupied by beads of tunnel.
\end{paragraph}

@@

\begin{figure}
  \centering
    \begin{tabular}{cc}
    \begin{minipage}{0.66\hsize}
    \centering
      \begin{tabular}{cc}
      \begin{minipage}{0.45\linewidth}
      \centering
        \begin{tikzpicture}
	\draw[white] (0:0) -- (120:1);
	\draw[white] (0:0) -- (-60:1);
	\draw[white] (0:0) -- (0:1);

@@

      \begin{minipage}{0.45\linewidth}
      \centering
        \begin{tikzpicture}
	\draw[white] (0:0) -- (0:1);
	\draw[white] (0:0) -- (120:1);
	\draw[white] (0:0) -- (-90:2);

@@

          \node at (0,-2) {Point $n_1$ is occupied};
        \end{tikzpicture}
      \end{minipage}
    \end{tabular}
    \caption{Exit of Tunnel}
    \label{TTT_tunnel_exit}
    \end{minipage}

    \begin{minipage}{0.33\hsize}
    \centering
     \begin{tikzpicture}
	\draw[white] (0:0) -- (120:1);
	\draw[white] (0:0) -- (-60:1);
            \fill[blue](0,0) circle [radius=0.05];
            \draw[blue] (0:1) circle [radius = 0.05];
            \draw[->] (0:0.1) -- node[above]{$p$} (0:0.9);

            \foreach \theta in {60, -60, 120,-120,180}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }
            \node[transform canvas={shift=(60:1)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
                \end{tikzpicture}

    \caption{Inside tunnel}
    \label{TTT_inside_tunnel}
    \end{minipage}

    \end{tabular}
\end{figure}
\end{proof}

\begin{proof}[lemma \ref{TTT_tunnelC_lemma}]
Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$.
Assume $S[h..i+1] = bt^{i-h}b (h<i)$. If at least one of $w[h+1..i]$ are stabilized by tunnel $C$, then only $w[h+1]$ can use tunnel $C$ because if $w[g]$ which is one of $w[h+2..i]$ is stabilized by tunnel $C$, $C_g$ is a terminal.

Let us consider kinds of stabilization $S[h-1..h+1] = tbt$ or $S[h-1..h+1] = bbt$ into follows. In result, $\#bc(C_{h-3}) > \#bc(C_{h+1})$. In addition according to lemma\ref{TTT_exit} $\#bc(C_{h+1}) \geq \#bc(C_{i})$. Thus, $\#bc(C_{h-3}) > \#bc(C_{i})$.
\\

\subsubsection{Case of $S[h-1..h+1] = tbt$}
Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.
